---
title: "Travel Assured analysis"
author: "Michal Lauer"
date: "`r format(as.Date('2022-10-27'), format = '%d.%m.%Y')`"
output:
  html_document:
    theme: paper
    css: "assets/css/style.css"
    df_print: kable
    highlight: zenburn
    code_folding: hide
editor_options:
  chunk_output_type: console
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_dir = "output/",
                    output_format = c("html_document", "pdf_document"))})
---
```{r include=F}
# Environment preparation
cat('\f')
rm(list = ls())
# Clear output
if (dir.exists("output") & !isTRUE(getOption('knitr.in.progress')))
  unlink("output", recursive = T)
# RMarkdown requirements for renv
require("rmarkdown")
require("yaml")
# knitr setting
knitr::opts_chunk$set(fig.align = "center",
                      fig.path = "output/imgs/",
                      fig.width = 12,
                      fig.height = 7,
                      dev = c("svg", "png"))
# gtsummary theme
gtsummary::set_gtsummary_theme(list(
  "style_number-arg:big.mark" = " "
))
```

# Preface
This analysis is done on generated data and does not represent a real company.
The main purpose of this work was to get my certification, which I've
[accomplished](https://www.datacamp.com/certificate/DA0016698068691). Now I use
this work to showcase my work and how I *do* data analysis. The project
is located on my [Github page](https://github.com/MichalLauer/TravelAssured)
```{r include=F}
#TODO: Přidat prezentaci
#TODO: Upravit prezentaci
```

# Introduction
Travel Assured is a travel insurance company. Due to the COVID pandemic,
they have had to cut their marketing budget by over 50%. It is more important
than ever that they advertise in the right places and to the right people.

Travel Assured wants answers to two key questions:

1) Are there differences in the travel habits between customers and non-customers?
2) What is the typical profile of customers and non-customers?

This analysis notebook's purpose is to introduce the analysis to a *data* person.
It shows how the data was manipulated, what was changed, and how things were
computed. For a more business-detail approach, see the attached presentation.

```{r include=F}
# TODO: Prezentace
```

# Libraries
This one block loads all libraries.
```{r libs, message=F, warning=F}
# Data wrangling
library(dplyr)
library(tidyr)
library(glue)

# Graphs
library(ggplot2)
library(patchwork)

# Tables
library(gtsummary)
```

# Data load
The raw data set is loaded and transformed into a tibble.
```{r data_raw}
data_raw <-
  read.csv(file = "input/travel_insurance.csv") |> 
  as_tibble()

head(data_raw)
```

The column names are transformed to *snake_case* stanard using the snakecase
package. Variables are then transformed, such that:

- *employment type* is now a factor
- *graduate or not* is a logical variable (true - graduated, false - did not
graduate)
- *chronic disease* is now a logical variable (true - has disease, false - does
not have a disease)
- *frequent flyer* is now a logical variable (true - is a frq. flr., false - is
not a frq. flr.)
- *ever travelled abroad* is now a logical variable (true - has travelled, false
- has not travelled)
- *travel insurance* is now a logical variable (true - is insured, false - is
not insured)
```{r data}
data <-
  data_raw |> 
  rename_with(snakecase::to_snake_case) |> 
  mutate(employment_type       = factor(employment_type),
         family_members        = family_members,
         graduate_or_not       = graduate_or_not == "Yes",
         chronic_diseases      = chronic_diseases == 1,
         frequent_flyer        = frequent_flyer == "Yes",
         ever_travelled_abroad = ever_travelled_abroad == "Yes",
         travel_insurance      = travel_insurance == 1)
```

The data is now translated and the overall look is shown below.
```{r }
skimr::skim_without_charts(data)
```

Form the overview, it can be seen that there are no missing values - which is 
really nice! Employment has only two levels - *Government Sector*, and 
*Private Sector/Self Employed*. Each customer can have up to 9 other family
members (excluding 1 as the factor starts at two family members). Except for
customers who have bought an insurance, all logical values are heavily
imbalanced. This could be useful in hypothesis testing and data exploration.
Finally, 

## Support variables {#vars}
For further data analysis, some help variables are created to reduce bugs.
```{r class.source = 'fold-show'}
# Columns assigned as Travel habits
travel_habits    <- c("frequent_flyer", "ever_travelled_abroad")
# Columns assigned as Customer profiles
customer_profile <- c("age", "employment_type", "graduate_or_not",
                      "annual_income", "family_members", "chronic_diseases",
                      "travel_insurance")
# Labels transformation
labels           <- c("TRUE" = "Yes", "FALSE" = "No")
```

# Difference in travel habits

The first business question that is asked is:

> Are there differences in the travel habits between customers and non-customers?

Two columns which identify travel habits are *frequent_flyer* and
*ever_travelled_abroad*.

## Frequent flyers

To identify if the difference among insured and uninsured people who are
frequent flyers and who are **not** frequent flyers, the p-value is calculated.
First the proportions are prepared in a special table.
```{r }
fq_prop <- 
  data |> 
  select(frequent_flyer, travel_insurance) |> 
  group_by(travel_insurance, frequent_flyer) |> 
  summarise(n = n(), .groups = "drop_last") |> 
  mutate(total = sum(n),
         mean = n/total)

fq_prop
```

Compute *p*-value where travel insurance is false.
```{r }
x <- fq_prop$n[1:2]
n <- fq_prop$total[1:2]

fq_prop_uninsured <- prop.test(x = x, n = n, correct = F)
fq_prop_uninsured
```

Compute *p*-value where travel insurance is true.
```{r }
x <- fq_prop$n[3:4]
n <- fq_prop$total[3:4]

fq_prop_insured <- prop.test(x = x, n = n, correct = F)
fq_prop_insured
```

The differences among insured and uninsured people is graphically displayed.
```{r frequent-flyers-bars}
# Prepare text for graph
fq_significance <- glue("
Significance of difference (alpha = 0.05)
  Insured customers: p {format.pval(fq_prop_insured$p.value)}
  Uninsured customer: p {format.pval(fq_prop_uninsured$p.value)}
")

fq_p1 <-
  data |> 
  select(frequent_flyer, travel_insurance) |> 
  ggplot(aes(x = travel_insurance, fill = frequent_flyer)) +
  geom_bar(position = "dodge") +
  annotate(geom = "label", x = 1.8, y = 1100,
           label = fq_significance, hjust = 0) +
  theme_bw() +
  scale_x_discrete(labels = labels) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1300),
                     labels = scales::label_number()) +
  scale_fill_discrete(labels = labels) +
  theme(
    panel.grid.major.x = element_blank(),
    plot.caption = element_text(face = "italic", size = 9),
    legend.position = "bottom",
    plot.title = element_text(size = 16)
  ) +
  labs(
    title = "The difference among customers is statistically significant",
    x = "Insured",
    y = "Total count",
    caption = "Source: Michal Lauer, laumi.me"
  )

fq_p1
```

The second bar plot show the proportion among insured and uninsured people.
```{r frequent-flyers-proportions}
fq_p2 <- 
  data |> 
  select(frequent_flyer, travel_insurance) |> 
  ggplot(aes(x = travel_insurance, fill = frequent_flyer)) +
  geom_bar(position = "fill") +
  theme_bw() +
  scale_x_discrete(labels = labels) +
  scale_y_continuous(expand = c(0, 0),
                     labels = scales::label_percent()) +
  scale_fill_discrete(labels = labels) +
  theme(
    panel.grid.major.x = element_blank(),
    plot.caption = element_text(face = "italic", size = 9),
    legend.position = "bottom",
    plot.title = element_text(size = 16)
  ) +
  labs(
    title = "Iregular flyers heavilly outweight regular flyers",
    x = "Insured",
    y = "Relative count",
    caption = "Source: Michal Lauer, laumi.me"
  )

fq_p2
```

Joined graphs using patchwork.
```{r frequent-flyers-merged}
# Edit graphs for patchwork
fq_p1_pw <- 
  fq_p1 +
  labs(title = NULL,
       caption = NULL)

fq_p2_pw <- 
  fq_p2 +
  labs(title = NULL,
       caption = NULL)

# Update annotate position
fq_p1_pw$layers[[2]]$data$x <- 1.35

# Build graph with patchwork
fq_patchwork <- 
  (fq_p1_pw + fq_p2_pw) / guide_area() +
  plot_layout(guides = "collect", heights = c(10, 1)) +
  plot_annotation(
    title = "Overview of frequent flyers among customers and non-customers",
    caption = "Source: Michal Lauer, laumi.me"
  ) & labs(
    fill = "Frequent flyers"
  ) &
  theme(plot.caption = element_text(face = "italic", size = 9))

fq_patchwork
```

## Ever travelled abroad
The second identified travel habit is whether a person has ever travelled
abroad. The process here is the same. First, the proportion table is created
so *p*-values can be computed.
```{r }
eta_prop <- 
  data |> 
  select(ever_travelled_abroad, travel_insurance) |> 
  group_by(travel_insurance, ever_travelled_abroad) |> 
  summarise(n = n(), .groups = "drop_last") |> 
  mutate(total = sum(n),
         mean = n/total)

eta_prop
```

Compute *p*-value where travel insurance is false.
```{r }
x <- eta_prop$n[1:2]
n <- eta_prop$total[1:2]

eta_prop_uninsured <- prop.test(x = x, n = n, correct = F)
eta_prop_uninsured
```

Compute *p*-value where travel insurance is true.
```{r label}
x <- eta_prop$n[3:4]
n <- eta_prop$total[3:4]

eta_prop_insured <- prop.test(x = x, n = n, correct = F)
eta_prop_insured
```

Now a bar graph is created representing the difference in each group.
```{r ever-travelled-abroad-bars}
# Prepare text for graph
eta_significance <- glue("
Significance of difference (alpha = 0.05)
  Insured customers: p {format.pval(eta_prop_insured$p.value)}
  Uninsured customer: p {format.pval(eta_prop_uninsured$p.value)}
")

eta_p1 <-
  data |> 
  select(ever_travelled_abroad, travel_insurance) |> 
  ggplot(aes(x = travel_insurance, fill = ever_travelled_abroad)) +
  geom_bar(position = "dodge") +
  annotate(geom = "label", x = 1.8, y = 1100,
           label = eta_significance, hjust = 0) +
  theme_bw() +
  scale_x_discrete(labels = labels) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1300),
                     labels = scales::label_number()) +
  scale_fill_discrete(labels = labels) +
  theme(
    panel.grid.major.x = element_blank(),
    plot.caption = element_text(face = "italic", size = 9),
    legend.position = "bottom",
    plot.title = element_text(size = 16)
  ) +
  labs(
    title = "The difference among customers is statistically significant",
    x = "Insured",
    y = "Total count",
    caption = "Source: Michal Lauer, laumi.me"
  )

eta_p1
```

The proportions are compares using filled bar graph.
```{r ever-travelled-abroad-props}
eta_p2 <- 
  data |> 
  select(ever_travelled_abroad, travel_insurance) |> 
  ggplot(aes(x = travel_insurance, fill = ever_travelled_abroad)) +
  geom_bar(position = "fill") +
  theme_bw() +
  scale_x_discrete(labels = labels) +
  scale_y_continuous(expand = c(0, 0),
                     labels = scales::label_percent()) +
  scale_fill_discrete(labels = labels) +
  theme(
    panel.grid.major.x = element_blank(),
    plot.caption = element_text(face = "italic", size = 9),
    legend.position = "bottom",
    plot.title = element_text(size = 16)
  ) +
  labs(
    title = "Iregular flyers heavilly outweight regular flyers",
    x = "Insured",
    y = "Relative count",
    caption = "Source: Michal Lauer, laumi.me"
  )

eta_p2
```

Joined graphs using patchwork.
```{r ever-travelled-abroad-merged}
# Edit graphs for patchwork
eta_p1_pw <- 
  eta_p1 +
  labs(title = NULL,
       caption = NULL)

eta_p2_pw <- 
  eta_p2 +
  labs(title = NULL,
       caption = NULL)

# Update annotate position
eta_p1_pw$layers[[2]]$data$x <- 1.35

# Build graph with patchwork
eta_patchwork <- 
  (eta_p1_pw + eta_p2_pw) / guide_area() +
  plot_layout(guides = "collect", heights = c(10, 1)) +
  plot_annotation(
    title = "Overview of frequent flyers among customers and non-customers",
    caption = "Source: Michal Lauer, laumi.me"
  ) & labs(
    fill = "Frequent flyers"
  ) &
  theme(plot.caption = element_text(face = "italic", size = 9))

eta_patchwork
```

# Customer profile
The second questions that the business asks is:

> What is the typical profile of customers and non-customers?

This questions is answered by summarizing columns related to customer profile 
[see here](#vars)

## Numerical
Overview of numerical characteristics.
```{r }
data |> 
  select(all_of(customer_profile)) |> 
  select(travel_insurance, where(is.numeric)) |> 
  mutate(travel_insurance = if_else(travel_insurance, "Insured", "Uninsured")) |> 
  tbl_summary(by = travel_insurance,
              label = list(
                age ~ "Age",
                annual_income ~ "Annual income",
                family_members ~ "# of family members"
              ),
              statistic = everything() ~ "{mean} ± {sd} ({median})",
              digits = everything() ~ 2,
              type = family_members ~ "continuous") |> 
  modify_caption("Characteristics of numerical variables") |> 
  add_p()
```

```{r }
#TODO: Summary
```

## Logical
Overview of logical characteristics.
```{r }
data |> 
  select(all_of(customer_profile)) |>
  select(travel_insurance, where(is.logical)) |> 
  mutate(travel_insurance = if_else(travel_insurance, "Insured", "Uninsured")) |> 
  tbl_summary(by = travel_insurance,
              label = list(
                graduate_or_not ~ "Graduated",
                chronic_diseases ~ "Has chronic disease"
              )) |> 
  modify_caption("Characteristics of logical variables") |> 
  add_p(pvalue_fun = function(x) style_number(x, digits = 2))
```

```{r }
#TODO: Summary
```

## Factor
Overview of factor characteristics.
```{r }
data |> 
  select(all_of(customer_profile)) |>
  select(travel_insurance, where(is.factor)) |> 
  mutate(travel_insurance = if_else(travel_insurance, "Insured", "Uninsured")) |> 
  tbl_summary(by = travel_insurance,
              label = employment_type ~ "Employment type") |> 
  modify_caption("Characteristics of factor variables") |> 
  add_p()
```

```{r }
#TODO: Summary
```
